Predicting Covid-19 Data

### 2022-12-06 powerpoint.rmd

* Create a random matrix : m X n
  * m = number of random outcomes (*chosen to be 150*)
  * n = number of observed days (*n = 1,...,j*)
* Each # in the matrix is a Gaussian distribution with mean = 1 and sigma = 0.1
  * multiply each column (*j*) by the # of total cases (or deaths) that corresponds to each day *j*
- add more...

>>>>

* Create a random matrix : m X n
  * m = number of random outcomes (*chosen to be 150*)
  * n = number of observed days (*n = 1,...,j*)
* Each # in the matrix is a Gaussian distribution with mean = 1 and sigma = 0.1
  * multiply each column (*j*) by the # of total cases (or deaths) that corresponds to each day *j*
